A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2020-08-10 vignette/191115_PMMB_DataWrangling_PM.Rmd
Note added about missing trials
remove checks from header

# Data wrangling
This file is not complete and there are a number of things that need checking
   - Mean squares are only calculated for the triazoles and controls
   - If the years for each trial are input correctly
   - If the disease and yield errors are calculated and that they are shuffled correctly into the data frame
   - AUDPC needs to be checked for starting dates and if trials have been omitted
   - Check that what is generated from this file matches the main file and update
   - write.csv should have row.names = FALSE

>>>>

# Data wrangling
## Non-wrangled trials

Data from the three follow trials were input manually from either PDF or word files.  
   - Gatton 2012  
   - Kingaroy 2012  
   - Emerald 2016
